Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-30 latex/appendix.tex
tex

\appendix

@@

	\item faster training (algorithm tweak) FAT/other | postpone

@@

	\item [?] Combine and even better. | Mixing ACT and AMDsemi does result
		in clearly better results. It's on par with AMDsemi.

@@

\subsection{Discarded or Rejected}

@@

	\item \xmark
		MSE attack? | TMA is already close enough to it.

>>>>

\newpage
\appendix

@@

@@

	\item [?] Combine and even better. | Mixing ACT and AMDsemi does result
		in clearly better results. It's on par with AMDsemi. Are they really
		that different?

@@

\subsection{Done, Discarded or Rejected}

@@

	\item [\xmark] MSE attack? | TMA is already close enough to it.

	\item [\xmark] Faster training (algorithm tweak) based FAT/other | this is
		a dead end. ACT has a different loss function to the outer minimization
		problem, and hence result in different gradient and we cannot reuse
		these gradients for algorithms like free adversarial training.
		Re-calculating the gradients we need would simple double the
		computational cost of the algorithm and diminish the gain from Free
		Adversarial Training. We are no longer using the core benefit of FAT in
		this way. In contrast, the AMD / AMDhm formulation can benefit from
		this setup. | Further experiments suggest very weak robustness and the
		models are very prone to collapse due to the non-zero initial delta
		(results in too hard adversarial example).  | gradient approximation
		does not look convincing. triplet gradient and ACT gradient does not
		look convertible.
